Modelling the innovation and extinction of archaeological ideas

### 2018-04-04 analysis/paper/citation-clusters/How-to-cluster-citations.Rmd
hairball for handout

title_word_pairs_to_plot %>% 
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "cyan4") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                point.padding = unit(0.2, "lines"),
                   size = 2) +
  theme_void()

ggsave(here::here('analysis/figures/graph_plot1.png'),
       h = 30,
       w = 30)
```

>>>>

title_word_pairs_to_plot %>% 
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "cyan4") +
  geom_node_text(aes(label = name), 
                 repel = TRUE,
                 point.padding = unit(0.2, "lines"),
                size = 1.2,
                segment.colour = "grey70",
                segment.alpha = 0.3
                ) +
  geom_node_point(size = 2,
                  alpha = 0.4) +
  theme_void() +
  theme(legend.position="none")

ggsave(here::here('analysis/figures/graph_plot1.pdf'),
       h = 8,
       w = 10.5,
       units = c("in")) # for paper 10 x 5, for poster 30x30
```
